---
title: "Penguin Body Mass Analysis"
author: "Nassiba Taib"
date: "2026-09-21"
---
## Introduction

In this post, I will explore the Palmer Penguins dataset and compare body mass among the three penguin species.

Data: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/), Palmer Station Antarctica LTER.


## Exploring the data

```{r}
#| message: false
#| warning: false

library(palmerpenguins)
library(dplyr)
library(ggplot2)

penguins
```


## Exploring the data

```{r}
library(palmerpenguins)
library(dplyr)
library(ggplot2)

penguins_clean <- penguins |>
  select(species, body_mass_g) |>
  filter(!is.na(body_mass_g))

penguins_clean
```


## Average body mass by species

```{r}
average_mass <- penguins_clean |>
  group_by(species) |>
  summarise(mean_body_mass_g = mean(body_mass_g))

average_mass
```


## Body mass comparison

```{r}
#| label: fig-body-mass
#| fig-cap: "Body mass distribution of Palmer Penguins by species."

ggplot(penguins_clean, aes(x = species, y = body_mass_g)) +
  geom_boxplot() +
  labs(
    x = "Species",
    y = "Body mass (g)"
  )
```

## Findings

The results show differences in body mass among the three penguin species. Gentoo penguins have a higher average body mass than Adelie and Chinstrap penguins. The boxplot also shows the distribution of body mass within each species.

